Analysis : exp249-253 analysis

### 2019-08-19 resistingrhythm/analysis/exp328-339.Rmd
Vis tweaks

```{r, fig.height=2.5, fig.width=2.25}
results %>% 
  filter(osc_rate < 1.5, freq < 150) %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(freq~kind, scales = "free")
```

@@

# H only plots
```{r, fig.height=1.3, fig.width=2.5}
results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  ggplot(aes(x=as.factor(osc_rate), y=rate_k, group=interaction(osc_rate, kind), color=kind)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  # lims(y=c(0, 100)) +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  facet_grid(.~freq, scales = "free")
```

@@

>>>>

# Plot all
```{r, fig.height=2.5, fig.width=2.25}
results %>% 
  filter(osc_rate < 1.5, freq < 150) %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(freq~kind, scales = "free")
```

@@

# H only plots
## Box
```{r, fig.height=1.3, fig.width=2.5}
results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  ggplot(aes(x=as.factor(osc_rate), y=rate_k, group=interaction(osc_rate, kind), color=kind)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  # lims(y=c(0, 100)) +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  facet_grid(.~freq, scales = "free")
```

@@

## Mean
```{r, fig.height=1.1, fig.width=2.6}
freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))

results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  geom_point() +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  lims(y=c(0, 100)) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  facet_grid(.~freq, scales = "free", labeller=freq_labels)
```

```{r, fig.height=1.1, fig.width=2.6}
results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
  geom_point() +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  theme_classic() +
  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  lims(y=c(0.0, .12)) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  labs(y="Kappa", x="Osc. rate", tag="b.")

```
